\sysfull

### 2017-08-11 paper/evaluation.tex
added explanation

We start with evaluating the efficiency of the \sys compiler Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging calls\todo{calls or code? what is paging call?}{Kiwan} in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%. The results indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, the \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer aliasing. Thus, it results in the \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provided in Section~\ref{sec:result_compiler_time}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise the compiler can be used to simplify the programmability.

>>>>

We start with evaluating the efficiency of the \sys compiler Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging macro ({\tt RVAR} and {\tt WVAR}) in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%. The results indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, the \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer aliasing. Thus, it results in the \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provided in Section~\ref{sec:result_compiler_time}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise the compiler can be used to simplify the programmability.
